\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-06 docs/paper/paper.tex
Processed Tom's feedback into annotations within the .tex file. Modified TODO list.

% Title
\title{\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}}
\author{
  \textbf{R. Janssen} - \href{mailto:ramon.janssen@student.ru.nl}{ramon.janssen@student.ru.nl} \\
  \textbf{T. de Ruijter} - \href{mailto:t.deruijter@student.ru.nl}{t.deruijter@student.ru.nl}\\
%  \textbf{T. Claassen} - \href{mailto:tomc@cs.ru.nl}{tomc@cs.ru.nl}\\
%  \textbf{M. Hinne} - \href{mailto:mhinne@cs.ru.nl}{mhinne@cs.ru.nl}
}

@@

\begin{abstract}
In this work we applied PC algorithm on resting-state data of healthy human subjects.
Additionally we propose a variant of PC algorithm that poses weaker assumptions on the model, better fitting the underlying model.
We find that detecting structure homological areas in the brain works better with PC algorithm than most conventional diffusion weighted imaging techniques.
In the area of directionality and causality, more research is needed.
\end{abstract}

@@

\subsection{Problem statement}
This work seeks to utilise the strengths of current state-of-the-art causal discovery methods by applying them to resting state brain fMRI data in order to find new applicable methods for determining causal patterns in the human brain.

@@

\subsection{Causal Discovery}
An approach for finding effective connectivity may be found in the domain of causal discovery.
A causal discovery method uses data about events to determine which of these events are correlated, and additionally, it attempts to determine which events cause which.
The definition of a causal relation is not trivial \cite[p.20]{spirtes2000} and the relevant principles will be covered in this section.
In our context, the causal discovery methods which have been used aim at inferring a Directed Acyclic Graph (DAG).
These can be interpreted from a probabilistic and a causal perspective.
%In our case, we consider graphs that also include non-directed edges, a so called Partial DAG (PDAG).

@@

\paragraph{Causal Markov Condition}
A set of variables represented by a causal DAG $G$ is probabilistically independent of its non-descendants (non-effects), conditioned on its parents (direct causes).

This means that there is some underlying causal process that can be represented as a DAG $G$, which is not necessarily observed.
The Causal Markov Condition also has a converse principle we also use to reason with causality.
It also means that in this process, there cannot be common causes of variables that are left out.

@@

This second condition means the graph correctly portrays the underlying probability distribution.
It enables us to reason about causality through reasoning with the graph through a phenomenon called directional separation.

@@

It is very unlikely that all events which are relevant for the causal graph are measured on a neuronal level; 
even with high temporal and spatial resolutions, the entire physiology of the brain is too complex to capture.
Modelling with causal insufficiency would seem more accurate.
In the underlying process, there exist V-structures $\left <X,L,Z \right>$ in which $L$ is latent.
When sampling from the observed distribution, we would find a relation $X \leftrightarrow Z$.
Since we assumed Causal Markov Conditionality, no feedback loops exist and all bi-directional arrows found must indicate existence of a latent confounder.

@@

\begin{algorithm}
\caption{PC algorithm}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{PC}{$data$}
\State connect all pairs of point in undirected graph $G$.
\Comment{Structural Part} 
\State $n \gets 0$
\While{there are connected pairs $X$, $Y$ such that $n < |\operatorname{Adjacencies}(X)\setminus\{Y\}| $}
  \ForAll{such connected pairs $X$, $Y$}
    \ForAll{subsets $S$ of $\operatorname{Adjacencies(X)}$ for which $|S| = n$}
      \If{$X$ and $Y$ are independent given $S$}
        \State remove edge $X - Y$ from G
        \State record $S$ as separating set of $X, Y$
        \State continue with the next pair $X$, $Y$
      \EndIf
    \EndFor
  \EndFor
  \State $n \gets n+1$
\EndWhile
\State $\text{PDAG} \gets G\text{, with all connections replaced by }\oline$
\Comment{Directional Part}
\ForAll{unshielded triples $\left <X, Y,Z \right> $ in $G$ }
  \If{$Y$ is not in the separating set of $X$ and $Z$}
    \State Orient $X \sline Y \sline Z$ as $X \srightarrow Y \sleftarrow Z$ in $\text{PDAG}$
  \EndIf
\EndFor
\State Apply other directionality rules from Spirtes et al. \cite[p.165-167]{spirtes2000}
\State \Return $G$ and the separating sets
\EndFunction
\end{algorithmic}
\end{spacing}
\label{alg:pc_alg}
\end{algorithm}

@@

% Conservative PC
\paragraph{Conservative PC}
The V-structure rule in PC algorithm orients unshielded triples based on a single separating set. 
Simply put, it is assumed the single found separating set is enough to show conditional independence. 
Ramsey et al. \cite{ramsey2012} introduce a weaker but still sufficient assumption for finding V-structures.
Through this weaker but still adjacency-faithful assumption, the method is more cautious than PC algorithm in drawing unambiguous conclusions on causal orientations.
That is why this method is named Conservative PC (CPC).
The resulting algorithmic changes provide better results and is able to mark incorrectly unshielded triples as unfaithful.
Sadly, CPC requires a significant amount of additional conditional independence tests, exponential in the largest branching degree of the tested structure.

% Multiple sepsets
\paragraph{Multiple Separating Sets}
The idea of CPC, to make a weaker assumption on graph faithfulness, is very potential.
Instead of doing additional tests, one could attempt to determine causal unfaithfulness with less dependency tests.
An adaptation to PC algorithm that would not increase the order of complexity is once a separating set is found, to test all other vertex subsets of the same order as well.
This finds all separating sets of the lowest order without increasing complexity.
Orienting an unshielded triple $\left<A,B,C\right>$ requires $B$ not to occur in any separating set of $(A,C)$.
By having more than one separating set, this constraint is strengthened.

@@

% Explicit test
A more explicit way to decrease faulty orientation of an unshielded triple $\left<A,B,C\right>$ is to check whether adding $B$ to a separating set of $(A,C)$ makes the pair conditionally dependent.
If so, the graph is likely to be more faithful to its modeled distribution.

@@

Also, the condition to orient $X - Y - Z$ according to the V-structure-rule has been made more strict.
As multiple separating sets have been found instead of only one, it needs to be checked whether $Y$ is in not in \emph{any} of those sets before the V-structure can be oriented.
Also, in addition to the original condition, $X$ and $Z$ are tested for d-separation given $\{Y\}$.
If they are found to be conditionally dependent, the triple is oriented as as $X \srightarrow Y \sleftarrow Z$.
As a final safe-guard, all unshielded triples are checked for unfaithfulness and marked as such if applicable using found separating sets. %TODO wat bedoel je hiermee?

\subsection{Pseudocode}
\label{sec:pseudocode}

@@

%\par\vfill\break % Omdat pseudocode veel hspace nodig heeft :(
%\advance\hsize by 8cm % Advance page height
%\advance\hoffset by -4cm % Shift top margin
%\floatevery{algorithm}{\setlength\hsize{15cm}}
%\floatevery{algorithmic}{\setlength\hsize{15cm}}
%TODO: meer hspace geven aan algorithms, alles hierboven werkte niet

\begin{algorithm}
\caption{Structure part of EMS-PC}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{Structure\_PC}{$data$}
\State connect all pairs of point in undirected graph $G$.
\State $n \gets 0$
\While{there are connected pairs $X$, $Y$ such that $n < |\operatorname{Adjacencies}(X)\setminus\{Y\}| $}
  \ForAll{such connected pairs $X$, $Y$}
    \ForAll{subsets $S$ of $\operatorname{Adjacencies(X)}$ for which $|S| = n$}
      \State test whether $X$ and $Y$ are d-separated given $S$
      \Comment{(Fisher-Z-test on $data$)}
      \If{$X$ and $Y$ are d-separated given $S$}
        \State remove the edge $X - Y$ from G
        \State record $S$ as a separating set of $X$ and $Y$
      \EndIf
    \EndFor
  \EndFor
  \State $n \gets n+1$

@@

\begin{algorithm}
\caption{Directional part of EMS-PC}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{Directional\_PC}{$G$, $sepsets$}
  \State $\text{PDAG} \gets G\text{, with all connections replaced by }\oline$
  \ForAll{unshielded triples $<X, Y, Z>$}
    \If{$Y$ is not in any separating set of $X$ and $Z \And X$ and $Z$ are dependent given $Y$}
      \Comment{V-structure-rule}
      \State Orient $X \sline Y \sline Z$ as $X \srightarrow Y \sleftarrow Z$ in $\text{PDAG}$
    \EndIf
  \EndFor
  \Repeat
    \ForAll{ordered, connected pairs $X$, $Y$}
      \Comment{Rule 1}
      \If{$X \osline Y$ or $X \sleftline Y$, and there is a node $Z$ such that $Z \srightarrow X$}
        \State Orient $X \sline Y$ as $X \rightarrow Y$
      \EndIf
      \Comment{Rule 2}
      \If{there is a directed path from $X$ to $Y$}
        \State Orient $X \sline Y$ as $X \srightarrow Y$
      \EndIf
    \EndFor
  \Until{no more edges are oriented}
  \State \Return PDAG
\EndFunction
\end{algorithmic}
\end{spacing}
\label{code:emsdirectional}
\end{algorithm}

@@

\subsection{Experimental validation}
% Section on how we plan on demonstrating the empirical value of research.
% Full description from step 1 to final data set
% TODO: Max: You asked me about my opinion on the identified structure, there was hardly any formal comparison. You could easily quantify this!To keep your study reproducible, you should not base your study on an (anonymous!) 'expert' :)
% TODO: ''dit product is dermatologisch getest' - en wat kwam UIT de test? Again, you should quantify this, and do not use an anonymous expert to prove the validity of  method. If you find this difficult (or impossible), try looking at things like consistency across permutations and/or subjects.'
Our analysis consisted of two parts, corresponding to the structural and directional parts of PC algorithm.
Firstly we discerned structure by using brain resting-state time series fMRI data with structure PC.
The generated structure is the same for all variants of PC discussed and proposed, as only the first separating set is used in finding unshielded triples.
We compared the generated structure with a Bayesian inference approach on finding structural connectivity from diffusion weighted imaging.
Comparison between structures is done visually with an expert on brain anatomy.
To increase the stability of found structures within subjects, we apply stability selection for different node permutations by Meinshausen and B{\"u}hlmann \cite{meinshausen2010}.
Multi-subject comparison was done by averaging and inspecting standard deviation over subjects.
% TODO: Inspecting and concluding what?

@@

\subsection{Data acquisition}
No explicit data acquisition was performed, instead we performed our analysis on the same data as treated by Hinne et al. in the aforementioned Bayesian structural analysis \cite{hinne2013, hinne2013structfunc}.

@@

\section{Results}
At first, we have applied modified PC on the structural connectivity data of six subjects.
To achieve stability, we have run the algorithm multiple times, in which the data was permuted randomly in each iteration.
The avarage of all iterations was used as a measure of certainty, i.e. how consistent the algorithm is for each point of data.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/struct_full}
  \includegraphics[width=0.5\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The structure on the left is found with the PC-algorithm, and the structure on the right is found by Hinne et al.}
\label{fig:struct_avg}
\end{figure}
In this matrix, higher values represent strong certainties of the presence of a connection.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_hemisphere_1_45}
  \caption{The average structure of the left hemisphere of all subjects, as found with PC.}
  \label{fig:struct_left}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_hemisphere_46_90}
  \caption{The average structure of the right hemisphere of all subjects, as found with PC.}
  \label{fig:struct_right}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_inter_hemisphere}
  \caption{The average structure between the two hemispheres of all subjects, as found with PC.}
  \label{fig:struct_inter_hemisphere}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_cerebellum}
  \caption{The average structure of the cerebellum of all subjects, as found with PC.}
  \label{fig:struct_cerebellum}
\end{figure}

@@

\section{Discussion}

The structural part of PC adds interesting information with respect to existing methods such as DWI.
Although DWI finds more structural data within homological areas, it does not find the corpus callosum, which is very clearly visible in the structure found with PC.
This is a known shortcoming of diffusion weighted imaging, as these connections are typically too long to measure correctly.
As such, causal discovery methods can contribute additional information to finding structural connectivity.

@@

% Further research
This does not necessarily imply that this data is noise, as communication between brain regions might actually differ per subject.
Activity of a brain region varies strongly over time and even though the subject have attempted to be in resting state, any thought or movement may cause signals to be measured.
This leads to inconsistent directional edges, even in an algorithm which finds causal relations correctly.
Further research may be done to investigating whether any of these arrows have a physiological meaning.
This can be done by repeating these experiment with more subjects to get a better view on the significance of the directional edges.

A Bayesian network cannot contain cycles, as that would imply that a variable is it's own ancestor and thus it's own cause.
The theory used here does not incorporate a temporal component and 
Ideally, a causal discovery methods finds only directed edges, resulting in a directed acyclic graph (DAG).
%In practice, however, often not all causal relations can be inferred and undirected edges are also used in a graph.
%As such, the result of a causal discovery method is a partially directed acyclic graph (PDAG).
As contemporary measuring techniques are too coarse and slow to model a brain at one point in time, correctly modelling variables over multiple points in time - opposing the acyclic assumption - would provide an interesting direction of further research.

It can also do this quite efficiently, as a few hundred iterations can be run in a matter of hours per subject.
We have not performed a statistical analysis on the number of iterations needed to stabilise the results.
It may be possible that a significant result can already be found with much less iterations.

% TODO: Suggereren task based analysis ipv resting state voor beter causaal beeld.

% TODO: Maak duidelijk welke aannames gedaan worden in welke PC variant en welke aannames verzwakt zouden kunnen worden.

\section{Acknowledgements}
We would like to thank Max Hinne and Tom Claassen, for without them this research would not have been viable.
They have provided us with ideas, valuable discussion and the data to perform actual research.

>>>>

% Title
\title{\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}}
\author{
  \textbf{R. Janssen} - \href{mailto:ramon.janssen@student.ru.nl}{ramon.janssen@student.ru.nl} \\
  \textbf{T. de Ruijter} - \href{mailto:t.deruijter@student.ru.nl}{t.deruijter@student.ru.nl}\\
%  \textbf{T. Claassen} - \href{mailto:tomc@cs.ru.nl}{tomc@cs.ru.nl}\\
%  \textbf{M. Hinne} - \href{mailto:mhinne@cs.ru.nl}{mhinne@cs.ru.nl}
}

@@

\begin{abstract}
% TODO: first state what you try to do, then how you did it, then what it brought you
In this work we applied PC algorithm on resting-state data of healthy human subjects.
Additionally we propose a variant of PC algorithm that poses weaker assumptions on the model, better fitting the underlying model.
We find that detecting structure homological areas in the brain works better with PC algorithm than most conventional diffusion weighted imaging techniques.
In the area of directionality and causality, more research is needed.
\end{abstract}

@@

\subsection{Problem statement}
% TODO: Tom: I am not a priori sure there are causal patterns in the human brain: what you try to do is see whether applying causal methods can help to bring new insights .. and perhaps to see if you can find evidence for the existence of such patterns.
This work seeks to utilise the strengths of current state-of-the-art causal discovery methods by applying them to resting state brain fMRI data in order to find new applicable methods for determining causal patterns in the human brain.

@@

\subsection{Causal Discovery}
An approach for finding effective connectivity may be found in the domain of causal discovery.
A causal discovery method uses data about events to determine which of these events are correlated, and additionally, it attempts to determine which events cause which.
% TODO: you say the definition of a causal relation is 'non-trivial' and that you will cover the 'relevant principles', but you don't actually say what you mean by 'a causal relation' (especially in the context of brain-connectivity)
The definition of a causal relation is not trivial \cite[p.20]{spirtes2000} and the relevant principles will be covered in this section.
In our context, the causal discovery methods which have been used aim at inferring a Directed Acyclic Graph (DAG).
These can be interpreted from a probabilistic and a causal perspective.
%In our case, we consider graphs that also include non-directed edges, a so called Partial DAG (PDAG).

@@

% TODO: relation CMC <-> unobserved common causes <-> 'causally insufficient models': I probably know what you try to say here, but that is not what it says right now
\paragraph{Causal Markov Condition}
A set of variables represented by a causal DAG $G$ is probabilistically independent of its non-descendants (non-effects), conditioned on its parents (direct causes).

This means that there is some underlying causal process that can be represented as a DAG $G$, which is not necessarily observed.
The Causal Markov Condition also has a converse principle we also use to reason with causality.
% TODO: Tom: what do you mean with the below?
It also means that in this process there cannot be common causes of variables that are left out.

@@

This second condition means the graph correctly portrays the underlying probability distribution.
It enables us to reason about causality through reasoning with the graph through the notion of directional separation.

@@

It is very unlikely that all events which are relevant for the causal graph are measured on a neuronal level; 
even with high temporal and spatial resolutions, the entire physiology of the brain is too complex to capture.
Modelling with causal insufficiency would seem more accurate.
% TODO: Tom: v-structures X -> L <- Z in which L is latent do not lead to X <-> Y.
% Us: then what does it lead to??

In the underlying process, there exist V-structures $\left <X,L,Z \right>$ in which $L$ is latent.
When sampling from the observed distribution, we would find a relation $X \leftrightarrow Z$.
Since we assumed Causal Markov Conditionality, no feedback loops exist and all bi-directional arrows found must indicate existence of a latent confounder.

@@

%TODO: Add line numbers
\begin{algorithm}
\caption{PC algorithm}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{PC}{$data$}
\State connect all pairs of point in undirected graph $G$.
\Comment{Structural Part} 
\State $n \gets 0$
\While{there are connected pairs $X$, $Y$ such that $n < |\operatorname{Adjacencies}(X)\setminus\{Y\}| $}
  \ForAll{such connected pairs $X$, $Y$}
    \ForAll{subsets $S$ of $\operatorname{Adjacencies(X)}$ for which $|S| = n$}
      \If{$X$ and $Y$ are independent given $S$}
        \State remove edge $X - Y$ from G
        \State record $S$ as separating set of $X, Y$
        \State continue with the next pair $X$, $Y$
      \EndIf
    \EndFor
  \EndFor
  \State $n \gets n+1$
\EndWhile
\State $\text{PDAG} \gets G\text{, with all connections replaced by }\oline$
\Comment{Directional Part}
\ForAll{unshielded triples $\left <X, Y,Z \right> $ in $G$ }
  \If{$Y$ is not in the separating set of $X$ and $Z$}
    \State Orient $X \sline Y \sline Z$ as $X \srightarrow Y \sleftarrow Z$ in $\text{PDAG}$
  \EndIf
\EndFor
\State Apply other directionality rules from Spirtes et al. \cite[p.165-167]{spirtes2000}
\State \Return $G$ and the separating sets
\EndFunction
\end{algorithmic}
\end{spacing}
\label{alg:pc_alg}
\end{algorithm}

@@

% Conservative PC
% TODO: Put conservative PC in the previous section and leave this section for our additions and ideas.
\paragraph{Conservative PC}
The V-structure rule in PC algorithm orients unshielded triples based on a single separating set. 
Simply put, it is assumed the single found separating set is enough to show conditional independence. 
Ramsey et al. \cite{ramsey2012} introduce a weaker but still sufficient assumption for finding V-structures.
Through this weaker but still adjacency-faithful assumption, the method is more cautious than PC algorithm in drawing unambiguous conclusions on causal orientations.
That is why this method is named Conservative PC (CPC).
The resulting algorithmic changes provide better results and is able to mark incorrectly unshielded triples as unfaithful.
Sadly, CPC requires a significant amount of additional conditional independence tests, exponential in the largest branching degree of the tested structure.

% Multiple sepsets
\paragraph{Multiple Separating Sets}
The idea of CPC, to make a weaker assumption on graph faithfulness, is very potential.
% TODO: Is very potential??
Instead of doing additional tests, one could attempt to determine causal unfaithfulness with less dependency tests.
An adaptation to PC algorithm that would not increase the order of complexity is once a separating set is found, to test all other vertex subsets of the same order as well.
This finds all separating sets of the lowest order without increasing complexity.
Orienting an unshielded triple $\left<A,B,C\right>$ requires $B$ not to occur in any separating set of $(A,C)$.
By having more than one separating set, this constraint is strengthened.

@@

% Explicit test
A more explicit way to decrease faulty orientation of an unshielded triple $\left<A,B,C\right>$ is to check whether adding $B$ to a separating set of $(A,C)$ makes the pair conditionally dependent.
If so, the graph is likely to be more faithful to its modeled distribution.
% TODO: What is meant with 'likely to be more fateful'? Quantify this.

@@

Also, the condition to orient $X - Y - Z$ according to the V-structure-rule has been made more strict.
As multiple separating sets have been found instead of only one, it needs to be checked whether $Y$ is in not in \emph{any} of those sets before the V-structure can be oriented.
Also, in addition to the original condition, $X$ and $Z$ are tested for d-separation given $\{Y\}$.
If they are found to be conditionally dependent, the triple is oriented as as $X \srightarrow Y \sleftarrow Z$.
As a final safe-guard, all unshielded triples are checked for unfaithfulness and marked as such if applicable using found separating sets. %TODO wat bedoel je hiermee?
% TODO: How do you mark unfaithful triples? can you spot the impact in the output?
\subsection{Pseudocode}
\label{sec:pseudocode}

@@

% TODO: How is this different from the first part of algorithm 1?
% TODO: Add line numbers
\begin{algorithm}
\caption{Structure part of EMS-PC}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{Structure\_PC}{$data$}
\State connect all pairs of point in undirected graph $G$.
\State $n \gets 0$
\While{there are connected pairs $X$, $Y$ such that $n < |\operatorname{Adjacencies}(X)\setminus\{Y\}| $}
  \ForAll{such connected pairs $X$, $Y$}
    \ForAll{subsets $S$ of $\operatorname{Adjacencies(X)}$ for which $|S| = n$}
      \State test whether $X$ and $Y$ are d-separated given $S$
      \Comment{(Fisher-Z-test on $data$)}
      \If{$X$ and $Y$ are d-separated given $S$}
        \State remove the edge $X - Y$ from G
        \State record $S$ as a separating set of $X$ and $Y$
      \EndIf
    \EndFor
  \EndFor
  \State $n \gets n+1$

@@

% TODO: Add line numbers
\begin{algorithm}
\caption{Directional part of EMS-PC}
\begin{spacing}{1.1}
\begin{algorithmic}
\Function{Directional\_PC}{$G$, $sepsets$}
  \State $\text{PDAG} \gets G\text{, with all connections replaced by }\oline$
  \ForAll{unshielded triples $<X, Y, Z>$}
    \If{$Y$ is not in any separating set of $X$ and $Z \And X$ and $Z$ are dependent given $Y$}
      \Comment{V-structure-rule}
      \State Orient $X \sline Y \sline Z$ as $X \srightarrow Y \sleftarrow Z$ in $\text{PDAG}$
    \EndIf
  \EndFor
  \Repeat
    \ForAll{ordered, connected pairs $X$, $Y$}
      \Comment{Rule 1}
      \If{$X \osline Y$ or $X \sleftline Y$, and there is a node $Z$ such that $Z \srightarrow X$}
        \State Orient $X \sline Y$ as $X \rightarrow Y$
      \EndIf
      \Comment{Rule 2}
      \If{there is a directed path from $X$ to $Y$}
        \State Orient $X \sline Y$ as $X \srightarrow Y$
      \EndIf
    \EndFor
  \Until{no more edges are oriented}
  \State \Return PDAG
\EndFunction
\end{algorithmic}
\end{spacing}
\label{code:emsdirectional}
\end{algorithm}

@@

\subsection{Experimental validation}
% Section on how we plan on demonstrating the empirical value of research.
% Full description from step 1 to final data set
% TODO: Tom: have you tested/verified whether or not your EMS-PC procedure is indeed 'more likely to be faithful'? (p6,l5)
% TODO: Max: You asked me about my opinion on the identified structure, there was hardly any formal comparison. You could easily quantify this!To keep your study reproducible, you should not base your study on an (anonymous!) 'expert' :)
% TODO: ''dit product is dermatologisch getest' - en wat kwam UIT de test? Again, you should quantify this, and do not use an anonymous expert to prove the validity of  method. If you find this difficult (or impossible), try looking at things like consistency across permutations and/or subjects.'
Our analysis consisted of two parts, corresponding to the structural and directional parts of PC algorithm.
Firstly we discerned structure by using brain resting-state time series fMRI data with structure PC.
The generated structure is the same for all variants of PC discussed and proposed, as only the first separating set is used in finding unshielded triples.
We compared the generated structure with a Bayesian inference approach on finding structural connectivity from diffusion weighted imaging.
Comparison between structures is done visually with an expert on brain anatomy.
To increase the stability of found structures within subjects, we apply stability selection for different node permutations by Meinshausen and B{\"u}hlmann \cite{meinshausen2010}.
Multi-subject comparison was done by averaging and inspecting standard deviation over subjects.
% TODO: Inspecting and concluding what?

@@

\subsection{Data acquisition}
% TODO: Huh? No data acquisition? Where do you get your results from then?
No explicit data acquisition was performed, instead we performed our analysis on the same data as treated by Hinne et al. in the aforementioned Bayesian structural analysis \cite{hinne2013, hinne2013structfunc}.

@@

\section{Results}
% TODO: I'm missing a clear answer to the question "did we manage to do what we set out to do"?
At first, we have applied modified PC on the structural connectivity data of six subjects.
To achieve stability, we have run the algorithm multiple times, in which the data was permuted randomly in each iteration.
The avarage of all iterations was used as a measure of certainty, i.e. how consistent the algorithm is for each point of data.

@@

% TODO: Add in caption what the reader is supposed to be looking at.
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{images/struct_full}
  \includegraphics[width=0.5\textwidth]{images/structure_max}
  \caption{The avarage structure of all subjects. The structure on the left is found with the PC-algorithm, and the structure on the right is found by Hinne et al.}
\label{fig:struct_avg}
\end{figure}
In this matrix, higher values represent strong certainties of the presence of a connection.

@@

% TODO: hard to compare or see what to look for -> "does it make sense or not"?
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_hemisphere_1_45}
  \caption{The average structure of the left hemisphere of all subjects, as found with PC.}
  \label{fig:struct_left}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_hemisphere_46_90}
  \caption{The average structure of the right hemisphere of all subjects, as found with PC.}
  \label{fig:struct_right}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_inter_hemisphere}
  \caption{The average structure between the two hemispheres of all subjects, as found with PC.}
  \label{fig:struct_inter_hemisphere}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics{images/struct_cerebellum}
  \caption{The average structure of the cerebellum of all subjects, as found with PC.}
  \label{fig:struct_cerebellum}
\end{figure}

@@

\section{Discussion}
The structural part of PC adds interesting information with respect to existing methods such as DWI.
Although DWI finds more structural data within homological areas, it does not find the corpus callosum, which is very clearly visible in the structure found with PC.
This is a known shortcoming of diffusion weighted imaging, as these connections are typically too long to measure correctly.
As such, causal discovery methods can contribute additional information to finding structural connectivity.

@@

% Further research
% TODO: What do you mean with this is not necessarily noise?
This does not necessarily imply that this data is noise, as communication between brain regions might actually differ per subject.
Activity of a brain region varies strongly over time and even though the subject have attempted to be in resting state, any thought or movement may cause signals to be measured.
This leads to inconsistent directional edges, even in an algorithm which finds causal relations correctly.
Further research may be done to investigating whether any of these arrows have a physiological meaning.
This can be done by repeating these experiment with more subjects to get a better view on the significance of the directional edges.

A Bayesian network cannot contain cycles, as that would imply that a variable is it's own ancestor and thus it's own cause.
The theory used here does not incorporate a temporal component and 
Ideally, a causal discovery methods finds only directed edges, resulting in a directed acyclic graph (DAG).
%In practice, however, often not all causal relations can be inferred and undirected edges are also used in a graph.
%As such, the result of a causal discovery method is a partially directed acyclic graph (PDAG).
% TODO: What do you mean with the below sentence?
As contemporary measuring techniques are too coarse and slow to model a brain at one point in time, correctly modelling variables over multiple points in time - opposing the acyclic assumption - would provide an interesting direction of further research.

% TODO: What do you mean with 'it can also do this'? What does 'this' refer to?
It can also do this quite efficiently, as a few hundred iterations can be run in a matter of hours per subject.
We have not performed a statistical analysis on the number of iterations needed to stabilise the results.
It may be possible that a significant result can already be found with much less iterations.

% TODO: Suggereren task based analysis ipv resting state voor beter causaal beeld. 
% TODO: Maak duidelijk welke aannames gedaan worden in welke PC variant en welke aannames verzwakt zouden kunnen worden.

% TODO: Tom suggereert dat dit te veel van het goede is.
\section{Acknowledgements}
We would like to thank Max Hinne and Tom Claassen, for without them this research would not have been viable.
They have provided us with ideas, valuable discussion and the data to perform actual research.
